### 2024-12-19 NLP/exercises.tex
Moved one exercise to 2021 exam to balance the two exams.
Shuffled the exercises to get three comparable exams.

\sheet{Lecture questions}

\begin{exercise}{NLP and the Web}
  \begin{enumerate}
    \item The web is an application area for NLP. Provide examples of applications.
    \item How can the web improve the quality of NLP? Provide examples.
  \end{enumerate}

  \begin{solution}
    \begin{enumerate}
      \item Information extraction, sentiment analysis, machine translation, question answering, etc.
      \item Web as a corpus, analyzing web-based knowledge repositories, extracting structured information, using web-scale data for training language models.
    \end{enumerate}
  \end{solution}
\end{exercise}

  \begin{solution}
    \begin{enumerate}
      \item NLP datasets are collections of annotated or unannotated text data designed for specific NLP tasks (e.g., sentiment analysis, translation). They serve as a foundation for training and testing machine learning models, enable reproducibility in research, and facilitate comparisons between models and techniques.
      \item Annotation process involves adding labels or metadata to text data (e.g., part-of-speech tags, sentiment labels). It improves model performance by providing high-quality training data, enables supervised learning by associating input with output labels, and impacts scalability and generalization of models depending on annotation quality.
      \item Strategies include task design (clearly define annotation tasks with examples and guidelines), platform selection (use platforms like Amazon Mechanical Turk or Prolific), quality control (use redundancy and include test questions to ensure reliability), and data aggregation (combine annotations using majority voting or statistical models).
    \end{enumerate}
  \end{solution}
\end{exercise}

  \begin{solution}
    \begin{enumerate}
      \item More features can lead to overfitting, require more training data, introduce noise, and slow down training and inference.
      \item Labeled training text (e.g., part-of-speech tags, named entity recognition).
    \end{enumerate}
  \end{solution}
\end{exercise}

\setcounter{section}{2022}
\sheet{1st exam}

@@

@@

\setcounter{section}{2020}
\sheet{1st exam}

@@

@@

\begin{exercise}{MRR and accuracy}
  \input{res/qa-answers.fig}
  Calculate MRR and Accuracy for the Question/Answering system in Figure \ref{fig:qa-answers}.

>>>>

\setcounter{section}{2022}\sheet{1st exam}

@@

\setcounter{section}{2021}\sheet{1st exam}

\begin{exercise}{NLP and the Web}
  \begin{enumerate}
    \item The web is an application area for NLP. Provide at least three examples of applications.
    \item How can the web improve the quality of NLP? Provide at least three examples.
  \end{enumerate}

  \begin{solution}
    \begin{enumerate}
      \item Information extraction, sentiment analysis, machine translation, question answering, …
      \item Web as a corpus, crowdsourcing annotations, multilingual data, …
    \end{enumerate}
  \end{solution}
\end{exercise}

  \begin{solution}
    \begin{enumerate}
      \item Collections of (possibly annotated) text data used for training and evaluating NLP models. They are crucial for developing and testing algorithms.
      \item Add metadata or linguistic labels to the text, which can be used for training supervised machine learning models. The quality of annotations directly impacts the performance of machine learning applications.
      \item Task design (clear instructions, examples), platform selection (e.g., Amazon Mechanical Turk), quality control (test questions, redundancy), data aggregation (majority voting, adjudication), and evaluation (inter-annotator agreement, error analysis).
    \end{enumerate}
  \end{solution}
\end{exercise}

  \begin{solution}
    \begin{enumerate}
      \item Overfitting, noise, and computational complexity can increase with the number of features, leading to poor generalization.
      \item Labeled training text (e.g., part-of-speech tags, named entity recognition).
    \end{enumerate}
  \end{solution}
\end{exercise}

@@

@@

\setcounter{section}{2020}\sheet{1st exam}

@@

\begin{exercise}{MRR and accuracy}
  \input{res/qa-answers.fig}
  Calculate Mean Reciprocal Rank (MRR) and Accuracy for the given query results in Figure \ref{fig:qa-answers} at $k=5$.
